\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2016-11-28 Response.tex

\documentclass[11pt]{article}
\usepackage[letterpaper,margin=1in,centering]{geometry}
\usepackage{amssymb}  
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{color}
\usepackage{bm}
\usepackage{xr}
\usepackage{hyperref}
\usepackage[]{cleveref} % get fancy referencing
% edit cref citations for IEEE format
\crefformat{equation}{(#2#1#3)} % no abbreviation for equation numbers
\Crefformat{equation}{Equation~(#2#1#3)} % no abbreviation for equation numbers
\crefrangeformat{equation}{(#3#1#4--#5#2#6)}
\Crefrangeformat{equation}{(#3#1#4--#5#2#6)}
\crefmultiformat{equation}{(#2#1#3)}{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}
% edit cref citations for IEEE format
\crefformat{figure}{Fig.~#2#1#3} % no abbreviation for equation numbers
\Crefformat{figure}{Fig.~#2#1#3} % no abbreviation for equation numbers
\crefrangeformat{figure}{Figs.~#3#1#4--#5#2#6}
\Crefrangeformat{figure}{Figs.~#3#1#4--#5#2#6}
\crefmultiformat{figure}{Figs.~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
% for items in a list
\crefformat{enumi}{(#2#1#3)}
\Crefformat{enumi}{Item~(#2#1#3)} 
\crefrangeformat{enumi}{(#3#1#4--#5#2#6)}
\Crefrangeformat{enumi}{Items~(#3#1#4--#5#2#6)}
\crefmultiformat{enumi}{(#2#1#3)}{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}

@@

\item \textit{The units of y axis of Figures 1 - 3 and 5 should be mentioned in the manuscript.}

The discussion of~\cref{fig:config_error} was updated to include:
\begin{correction}
    The horizontal axes of~\cref{fig:config_error} represent the spherical angles \( \lambda \) and \( \beta \), while the vertical axes represent the unitless magnitude of the error functions defined in~\cref{eqn:psi,eqn:A,eqn:B}.
\end{correction}
\item \textit{Please check and correct Page 2 Line 60.}
\item \textit{The units of the parameters are missing. These should be added in the manuscript.}
\item \textit{What are the design parameters of the proposed method and how the design parameters are selected? These should be included in the manuiscript.}
\item \textit{Specification of the sensors in the experiments should be included in the manuscript.}
\end{enumerate}

### 2016-11-29 Response.tex

\item \textit{The units of y axis of Figures 1 - 3 and 5 should be mentioned in the manuscript.}

The discussion of~\cref{fig:config_error} was updated to include:
\begin{correction}
    The horizontal axes of~\cref{fig:config_error} represent the domain of the spherical angles \( \lambda \) and \( \beta \) in degrees, while the vertical axes represent the unitless magnitude of the error functions defined in~\cref{eqn:psi,eqn:A,eqn:B}.    
\end{correction}
\item \textit{Please check and correct Page 2 Line 60.}
\item \textit{The units of the parameters are missing. These should be added in the manuscript.}
\item \textit{What are the design parameters of the proposed method and how the design parameters are selected? These should be included in the manuiscript.}
\item \textit{Specification of the sensors in the experiments should be included in the manuscript.}
\end{enumerate}

### 2016-11-29 manuscript.tex
Start addressing reviewer 4 #2. Include units for axes
Add units for figure 1. Address reviewer 4 #2
Add units for disturbance

\Cref{eqn:psi} is composed of an attractive term, \( A (R) \) toward the desired attitude, and a repulsive term, \( B(R) \) away from the undesired direction \( R^T v \).
In order to visualize the attitude error function on \( \SO \), we utilize a spherical coordinate representation.
Recall, that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
This coordinate system is commonly used to define locations on the Earth in terms of a latitude and longitude.
Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
\begin{figure}[H]%
    \centering 
    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.45\columnwidth]{attract_error} }~
    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.45\columnwidth]{avoid_error} }\\%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
    \subfigure[Configuration \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.45\columnwidth]{combined_error} }%
    \caption{Configuration error function visualization}
    \label{fig:config_error} 
\end{figure}%
We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \). 
Using the elementary Euler rotations, the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
Applying this method,~\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
The attractive error function, given by~\cref{eqn:A}, has been previously used for attitude control on \(\SO\).
The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).

@@

The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\). 
The desired state is \( R_d = I,\Omega_d = 0\).
\begin{figure}[H] 
    \centering 
    \subfigure[Attitude error vector \(e_R\) \label{fig:eR_con}]{\includegraphics[width=0.5\columnwidth]{eR_con}  }~
    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.5\columnwidth]{figures/Psi_con.pdf} }
    \subfigure[Angle to constraints \label{fig:con_angles_con}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_con.pdf} }  
    \caption{Attitude stabilization without adaptive update law}
    \label{fig:con} 
\end{figure}
We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \), with the function \( W(R,\Omega) = I \).
This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
\begin{figure}[H] 
	\centering 
    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.5\columnwidth]{Psi_adapt} }~
    \subfigure[Angle to constraints \label{fig:con_angles}]{\includegraphics[width=0.5\columnwidth]{constraint_angles} }\\
    \subfigure[Disturbance estimate \( \bar \Delta \)  \label{fig:delta_adapt} ]{\includegraphics[width=0.5\columnwidth]{Delta_adapt}}~
    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim=9cm 2.5cm 0 0,clip,width=0.645\columnwidth]{cad_adapt} }
	\caption{Attitude stabilization with adaptive update law}
	\label{fig:adapt} 
\end{figure}

>>>>

\Cref{eqn:psi} is composed of an attractive term, \( A (R) \) toward the desired attitude, and a repulsive term, \( B(R) \) away from the undesired direction \( R^T v \).
In order to visualize the attitude error function on \( \SO \), we utilize a spherical coordinate representation.
Recall, that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
This coordinate system is commonly used to define locations on the Earth in terms of a latitude and longitude.
Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
\begin{figure}[H]%
    \centering 
    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.45\columnwidth]{attract_error} }~
    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.45\columnwidth]{avoid_error} }\\%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
    \subfigure[Configuration \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.45\columnwidth]{combined_error} }%
    \caption{Configuration error function visualization}
    \label{fig:config_error} 
\end{figure}%
We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \). 
Using the elementary Euler rotations, the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
Applying this method,~\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
The horizontal axes of~\cref{fig:config_error} represent the domain of the spherical angles \( \lambda \) and \( \beta \) in degrees, while the vertical axes represent the unitless magnitude of the error functions defined in~\cref{eqn:psi,eqn:A,eqn:B}.
The attractive error function, given by~\cref{eqn:A}, has been previously used for attitude control on \(\SO\).
The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).

@@

The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\). 
The desired state is \( R_d = I,\Omega_d = 0\).
\begin{figure}[H] 
    \centering 
    \subfigure[Attitude error vector \(e_R\) \label{fig:eR_con}]{\includegraphics[width=0.5\columnwidth]{eR_con}  }~
    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.5\columnwidth]{figures/Psi_con.pdf} }
    \subfigure[Angle to constraints \label{fig:con_angles_con}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_con.pdf} }  
    \caption{Attitude stabilization without adaptive update law}
    \label{fig:con} 
\end{figure}
We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \si{\newton\meter}\), with the function \( W(R,\Omega) = I \).
This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
\begin{figure}[H] 
	\centering 
    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.5\columnwidth]{Psi_adapt} }~
    \subfigure[Angle to constraints \label{fig:con_angles}]{\includegraphics[width=0.5\columnwidth]{constraint_angles} }\\
    \subfigure[Disturbance estimate \( \bar \Delta \)  \label{fig:delta_adapt} ]{\includegraphics[width=0.5\columnwidth]{Delta_adapt}}~
    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim=9cm 2.5cm 0 0,clip,width=0.645\columnwidth]{cad_adapt} }
	\caption{Attitude stabilization with adaptive update law}
	\label{fig:adapt} 
\end{figure}
